Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-02-28 paper_comparison/paper_comparison/paper_comparison.Rmd
rearrange the topics
tweaking start of paper

Diagnosing a model is the key to determining whether there is anything importantly wrong. In linear regression analysis, residuals are typically examined for model diagnostics. Residuals summarise what is not captured by the model, and thus provide the capacity to identify what might be wrong.

@@

# Caluculation of p-value, effect size and power

Visual inference is

To be able to properly compare conventional tests to visual tests, we need to define the effect size of the residual departure, the power of the tests under a certain level of effect size,

### Caluculation of effect size

### Caluculation of p-value

@@

### Caluculation of power

@@

>>>>

Diagnostics are the key to determining whether there is anything importantly wrong with a model. In linear regression analysis, residuals from the model fit are commonly used. Residuals summarise what is not captured by the model, and thus provide the capacity to identify what might be wrong.

@@

# Caculation of p-value and power

## $p$-value

@@

## Power

@@

## Effect size

### 2023-02-28 paper_comparison/paper_comparison/paper_comparison.tex
tweaking start of paper

For non-linearity patterns, the power curve of RESET test climbs
aggressively from 10\% to 100\% as \(log_e(E)\) increases from 0 to 2.5,
while power of other tests respond inactively to the change of effect,
showing that RESET test is way more sensitive to the type of model
defects that being considered. Meanwhile, no noticeable residual
departures can be spotted from the example residual plots.

>>>>

For non-linearity patterns, the power curve of RESET test climbs
aggressively from 16\% to 100\% as \(log_e(E)\) increases from 0 to 2.5,
while power of other tests respond inactively to the change of effect,
showing that RESET test is way more sensitive to the type of model
defects that being considered. Meanwhile, no noticeable residual
departures can be spotted from the example residual plots.
